\texttt{thornado}-transport: IMEX schemes for two-moment neutrino transport respecting Fermi-Dirac statistics

### 2018-11-04 Documents/M1/Astronum_2018/sections/TimeIntegration.tex
Some edtis on time integration

\ee{Move definition of coefficients $c_{ij}$ and $\tilde{c}_{ij}$ here}

\subsection{Diffusion Accurate, Constraint-Preserving Implicit-Explicit Schemes}
Diffusion accurate is the other property the time integration should have.
In the diffusion limit, the distribution function is nearly isotropic so that $\vect{\cK}\approx\f{1}{3}\,\cJ\,\vect{I}$ and $\vect{\cH}\approx-\f{1}{3}\,\tau\,\nabla\cJ$.
The moment behavior are governed by (e.g., \cite{jinLevermore_1996})
\begin{equation}
  \pd{\cJ}{t} + \nabla\cdot\vect{\cH} = 0
  \quad\text{and}\quad
  \vect{\cH} = - \tau\,\nabla\cdot\vect{\cK}.  
  \label{eq:diffusionLimit}
\end{equation}
In the context of IMEX schemes, the above relationships imply that the relation $A\,\vec{\vect{\cH}}=-\f{1}{3}\,\tau\,\tilde{A}\,\nabla\vec{\cJ}$ should hold. 
We derived the diffusion accurate condition in \cite{chu_etal_2018} and proved that only type~ARS (investigated by Ascher, Ruuth, and Spiteri\cite{ascher_etal_1997}) IMEX schemes can be our candidates.

@@

>>>>

\ee{Move definition of coefficients $c_{ij}$ and $\tilde{c}_{ij}$ here.}
\ee{Discuss non-existence of high-order convex invariant scheme without explicit time step.}

\subsection{Diffusion Accurate, Constraint-Preserving Implicit-Explicit Schemes}

Diffusion accurate is the other property the time integration should have.
In the diffusion limit, the distribution function is nearly isotropic so that $\vect{\cK}\approx\f{1}{3}\,\cJ\,\vect{I}$ and $\vect{\cH}\approx-\f{1}{3}\,\tau\,\nabla\cJ$.
The moment behavior are governed by (e.g., \cite{jinLevermore_1996})
\begin{equation}
  \pd{\cJ}{t} + \nabla\cdot\vect{\cH} = 0
  \quad\text{and}\quad
  \vect{\cH} = - \tau\,\nabla\cdot\vect{\cK}.  
  \label{eq:diffusionLimit}
\end{equation}
In the context of IMEX schemes, the above relationships imply that the relation $A\,\vec{\vect{\cH}}=-\f{1}{3}\,\tau\,\tilde{A}\,\nabla\vec{\cJ}$ should hold. 
We derived the diffusion accurate condition in \cite{chu_etal_2018} and proved that only type~ARS (investigated by Ascher, Ruuth, and Spiteri\cite{ascher_etal_1997}) IMEX schemes can be our candidates.

\ee{Discuss conditions on IMEX coefficients for diffusion accuracy here.}

@@

\ee{Maybe make a separate subsection combining results from previous sections here.}
\ee{Need to motivate resorting to first-order accuracy.}
